### 2020-08-12 cases_and_policies/rmd/cf-pindex.Rmd
Added counterfactuals with pindex

---
title       : "Causal impact of masks, policies, behavior on early COVID-19 pandemic in the U.S."
subtitle    : "Counterfactuals"
author      :  Victor Chernozhukov, Paul Schrimpf, Hiro Kasahara
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        #css : 628notes.css
        code_folding: hide
        #lib_dir : deps
        self_cononontained : true
        fig_width: 8
        fig_height: 6
---

@@

```{r cffuncs, cache=FALSE}
source(paste(rootdir,"cases_and_policies/rmd/counterfactuals.R", sep="/"))
```

@@

rerunsim=FALSE
if (!file.exists("cfnop.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(sdf$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel,data=sdf))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop.Rda")
}
load("cfnop.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

@@

# ```{r nop-state-figures, cache=TRUE, warning=FALSE}
# states <- c("Washington","Illinois","Massachusetts")
# for(st in states) {
#   f <- cfplots(st, cfnop, data=df)
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figdp)
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figd + ylim(c(-1,5)))
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figl)
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figp)
#   dev.off()
# }
# ```

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dgrowth_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dcases_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-rel_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

## Non-Essential Business Closures

```{r business_sim, cache=FALSE}
# remove non essential business closure
cf <- sdf
cf[,"pnonessential"] <- 0
nobmodel <- createforwardsim(m, cf)

if (!file.exists("cfnb.Rda") || rerunsim) {
  cfnblist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=nobmodel, data=sdf))
  nball <- rbindlist(lapply(cfnblist, getmeans))
  save(cfnblist,nball, file="cfnb.Rda")
}
load("cfnb.Rda")
cfnb <- do.call(rbind, lapply(cfnblist, function(x) x$edf))
```

```{r, cache=TRUE}
cfnb <- merge(cfnb, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfnb, data=df)
  f$figp + ggtitle(sprintf("Effect of never shutting down non-essential businesses in %s",st))
  #grid.arrange(f$figd + ggtitle(), f$figdp + ggtitle(), nrow=2, top =
  #textGrob(st,gp=gpar(fontsize=20,font=2)))

  figdev(sprintf("%s/tex/tables_and_figures/%s-nb-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nb-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

figs <- nationalplots(nball, cfnb,
                      "never shutting down non-essential\nbusinesses")

figdev(paste(rootdir,"tex/tables_and_figures/us-nb-dgrowth_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nb-dcases_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nb-rel_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

if (!file.exists("cfmask.Rda") || rerunsim) {
  cfmasklist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=maskmodel, data=sdf))
  maskall <- rbindlist(lapply(cfmasklist, getmeans))
  save(cfmasklist, maskall, file="cfmask.Rda")
}
load("cfmask.Rda")
cfmask <- do.call(rbind, lapply(cfmasklist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dgrowth_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dcases_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-rel_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

rerunsim <- FALSE
if (!file.exists("cfmask1.Rda") || rerunsim) {
  cfmasklist1 <- lapply(unique(df$state),
                        function(s) nopstatesim(s,simobs=simmodel1,simcf=maskmodel1, data=sdf, nresid=1))
  maskall1 <- rbindlist(lapply(cfmasklist1, getmeans))
  save(cfmasklist1, maskall1, file="cfmask1.Rda")
}
load("cfmask1.Rda")
cfmask1 <- do.call(rbind, lapply(cfmasklist1, function(x) x$edf))

@@

if (!file.exists("cfshelter.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfshelter.Rda")
}
load("cfshelter.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dgrowth_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dcases_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-rel_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

rerunsim=FALSE
if (!file.exists("cfnop_deaths.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(df$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel, data=sdf, var="logdd", dvar="dlogdd"))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop_deaths.Rda")
}
load("cfnop_deaths.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dgrowth_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dcases_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-rel_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

## Non Essential Business Closures

```{r business_sim-deaths, cache=FALSE}
# remove non essential business closure
cf <- sdf
cf[,"pnonessential"] <- 0
nobmodel <- createforwardsim(m, cf, dvar="dlogdd", var="logdd")

if (!file.exists("cfnb_deaths.Rda") || rerunsim) {
  cfnblist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=nobmodel, data=sdf, var="logdd", dvar="dlogdd"))
  nball <- rbindlist(lapply(cfnblist, getmeans))
  save(cfnblist,nball, file="cfnb_deaths.Rda")
}
load("cfnb_deaths.Rda")
cfnb <- do.call(rbind, lapply(cfnblist, function(x) x$edf))
```

```{r, cache=TRUE}
cfnb <- merge(cfnb, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfnb, yvar="deaths", data=df)
  f$figp + ggtitle(sprintf("Effect of never shutting down non-essential businesses in %s",st))
  #grid.arrange(f$figd + ggtitle(), f$figdp + ggtitle(), nrow=2, top =
  #textGrob(st,gp=gpar(fontsize=20,font=2)))

  figdev(sprintf("%s/tex/tables_and_figures/%s-nb-dgrowth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nb-dcases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

figs <- nationalplots(nball, cfnb,
                      "never shutting down non-essential\nbusinesses", yvar="deaths")

figdev(paste(rootdir,"tex/tables_and_figures/us-nb-dgrowth_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nb-dcases_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nb-rel_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

if (!file.exists("cfmask_deaths.Rda") || rerunsim) {
  cfmasklist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=maskmodel, data=sdf, var="logdd", dvar="dlogdd"))
  maskall <- rbindlist(lapply(cfmasklist, getmeans))
  save(cfmasklist, maskall, file="cfmask_deaths.Rda")
}
load("cfmask_deaths.Rda")
cfmask <- do.call(rbind, lapply(cfmasklist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dgrowth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dgrowth_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dcases_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-rel_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

if (!file.exists("cfshelter_deaths.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfshelter_deaths.Rda")
}
load("cfshelter_deaths.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dgrowth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dgrowth_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dcases_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-rel_deaths_v1.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

>>>>

---
title       : "Causal impact of masks, policies, behavior on early COVID-19 pandemic in the U.S."
subtitle    : "Counterfactuals (with policies averaged)"
author      :  Victor Chernozhukov,  Hiro Kasahara, Paul Schrimpf
job         :
date        : "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "covid.bib"
link-citations: true
always_allow_html: true
output      :
    html_document :
        toc : true
        toc_depth : 3
        toc_float : true
        number_sections : true
        #theme : journal
        #css : 628notes.css
        code_folding: hide
        #lib_dir : deps
        self_cononontained : true
        fig_width: 8
        fig_height: 6
---

@@

```{r cffuncs, cache=FALSE}
source(paste(rootdir,"cases_and_policies/rmd/counterfactuals.R", sep="/"))
pols <- c("pmaskbus","pk12","pindex")
```

@@

rerunsim=FALSE
if (!file.exists("cfnop_idx.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(sdf$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel,data=sdf))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop_idx.Rda")
}
load("cfnop_idx.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

@@

# ```{r nop-state-figures, cache=TRUE, warning=FALSE}
# states <- c("Washington","Illinois","Massachusetts")
# for(st in states) {
#   f <- cfplots(st, cfnop, data=df)
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_idx.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figdp)
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_idx.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figd + ylim(c(-1,5)))
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_idx.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figl)
#   dev.off()
#
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figp)
#   dev.off()
# }
# ```

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dgrowth_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dcases_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-rel_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

if (!file.exists("cfmask_idx.Rda") || rerunsim) {
  cfmasklist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=maskmodel, data=sdf))
  maskall <- rbindlist(lapply(cfmasklist, getmeans))
  save(cfmasklist, maskall, file="cfmask_idx.Rda")
}
load("cfmask_idx.Rda")
cfmask <- do.call(rbind, lapply(cfmasklist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dgrowth_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dgrowth_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dcases_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-rel_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

rerunsim <- FALSE
if (!file.exists("cfmask1_idx.Rda") || rerunsim) {
  cfmasklist1 <- lapply(unique(df$state),
                        function(s) nopstatesim(s,simobs=simmodel1,simcf=maskmodel1, data=sdf, nresid=1))
  maskall1 <- rbindlist(lapply(cfmasklist1, getmeans))
  save(cfmasklist1, maskall1, file="cfmask1_idx.Rda")
}
load("cfmask1_idx.Rda")
cfmask1 <- do.call(rbind, lapply(cfmasklist1, function(x) x$edf))

@@

if (!file.exists("cfshelter_idx.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfshelter_idx.Rda")
}
load("cfshelter_idx.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dgrowth_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dgrowth_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dcases_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-rel_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

rerunsim=FALSE
if (!file.exists("cfnop_deaths_idx.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(df$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel, data=sdf, var="logdd", dvar="dlogdd"))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop_deaths_idx.Rda")
}
load("cfnop_deaths_idx.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dgrowth_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-dcases_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-nop-rel_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

if (!file.exists("cfmask_deaths_idx.Rda") || rerunsim) {
  cfmasklist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=maskmodel, data=sdf, var="logdd", dvar="dlogdd"))
  maskall <- rbindlist(lapply(cfmasklist, getmeans))
  save(cfmasklist, maskall, file="cfmask_deaths_idx.Rda")
}
load("cfmask_deaths_idx.Rda")
cfmask <- do.call(rbind, lapply(cfmasklist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dgrowth_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-mask-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dgrowth_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-dcases_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-mask-rel_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

if (!file.exists("cfshelter_deaths_idx.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfshelter_deaths_idx.Rda")
}
load("cfshelter_deaths_idx.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

@@

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dgrowth_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-shelter-dcases_deaths_idx.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

@@

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dgrowth_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-dcases_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-shelter-rel_deaths_idx.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()
